### 2015-11-13 Report/mse_formulation.tex
updated response document and manuscript

In the second method, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{equation} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{equation}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Plugging the \ac{MMSE} receivers in \eqref{eqn-10} into the \ac{MSE} expression in \eqref{mse-error} and into the \ac{SINR} expression in \eqref{eq:SINR}, we arrive at the following relation between the \ac{MSE} and the \ac{SINR} as
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. Note that the receive beamformers based on the \ac{MMSE} criterion are independent of the choice of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.

@@

The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is non-convex even for the fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}. Again we resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using the first order Taylor approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
\label{mse-lin}
\end{IEEEeqnarray}

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receivers. The optimization subproblem to find transmit precoders for fixed \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
The optimal transmit precoders for fixed receivers are obtained by solving the subproblem \eqref{eqn-mse-2} iteratively and by updating the fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} from the previous iteration until termination as discussed in Section \ref{sec-3.2.1}.

In all simulations, objective sequence generated by Algorithm \ref{algo-1} converges. \reviewF{However, for formal convergence analysis, following modifications are assumed. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective in \eqref{mod_obj}, which exhibits strong convexity. (ii) Moreover, for some large \eqn{B_{\max} \gg P_{\max}}, we limit \eqn{\beta_{l,k,n}} as \eqn{\beta_{l,k,n} \leq B_{\max}} without altering the solution, to ensure the feasible sets of \eqref{eqn-9} and \eqref{eqn-9--1} bounded. The additional constraint on \eqn{\beta_{l,k,n}} is necessary, since \eqref{eqn-6.3} need not be tight when \eqn{\gamma_{l,k,n} \to 0}. Due to this, \eqn{\beta_{l,k,n}} becomes unbounded, since any value of \eqn{\beta_{l,k,n}} satisfying \eqref{eqn-6.3} with inequality, satisfies \eqref{eqn-6.3} with equality. Finally, with these changes, convergence of Algorithm \ref{algo-1} is dealt in Appendix \ref{sec-3.5}.}

>>>>

In the second method, we solve the \ac{JSFRA} problem by exploiting the relation between the \ac{MSE} and the achievable \ac{SINR} when the \ac{MMSE} receivers are used at the user terminals \cite{mse_duality,christensen2008weighted}. The \ac{MSE} \me{\epsilon_{l,k,n}}, for a data symbol \me{d_{l,k,n}} is given by
\iftoggle{single_column}{
\begin{equation} \label{mse-error}
	\mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{equation}}{\allowdisplaybreaks
\begin{multline} \label{mse-error}
 \mathbb{E} \big [ ( d_{l,k,n} - \hat{d}_{l,k,n} )^2 \big ] = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 \\
 + \sum_{\mathclap{(j,i) \neq (l,k)}} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_i,k,n} \mvec{m}{j,i,n} \right |^2 + \enoise = \epsilon_{l,k,n}
\end{multline}}
where \me{\hat{d}_{l,k,n}} is the estimate of the transmitted symbol. Plugging the \ac{MMSE} receivers in \eqref{eqn-10} into the \ac{MSE} expression in \eqref{mse-error} and into the \ac{SINR} expression in \eqref{eq:SINR}, we arrive at 
\begin{equation} \label{eqn-mse-eq}
\epsilon_{l,k,n} = (1 + \gamma_{l,k,n})^{-1}.
\end{equation}
The above equivalence is valid only if the receivers are based on the \ac{MMSE} criterion. Using the equivalence in \eqref{eqn-mse-eq}, the \ac{WSRM} objective can be reformulated as the \ac{WMMSE} to obtain the precoders for the \acs{MU}-\acs{MIMO} scenario as discussed in \cite{christensen2008weighted,wmmse_shi,hong2012decomposition}. Note that the receive beamformers based on the \ac{MMSE} criterion are independent of the choice of the \me{\ell_q} norm used in the objective function to obtain the optimal transmit precoders \me{\mvec{m}{l,k,n}}.

@@

The alternative \ac{MSE} formulation given by \eqref{eqn-mse-1} is nonconvex even for a fixed \me{\mvec{w}{l,k,n}} due to the constraint \eqref{eqn-mse-1.2}. Again we resort to the \ac{SCA} approach \cite{marks1978technical} by relaxing the constraint by a sequence of convex subsets using the first order Taylor approximation around a fixed \ac{MSE} point \me{\tilde{\epsilon}_{l,k,n}} as
\begin{IEEEeqnarray}{rCl}
- \log_2(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\log(2) \, \tilde{\epsilon}_{l,k,n}} &\geq& t_{l,k,n}
\label{mse-lin}
\end{IEEEeqnarray}

Using the above approximation for the rate constraint, the problem defined in \eqref{eqn-mse-1} is solved for optimal transmit precoders \me{\mvec{m}{l,k,n}}, \acp{MSE} \me{\epsilon_{l,k,n}}, and the user rates over each sub-channel \me{t_{l,k,n}} for fixed receivers. The optimization subproblem to find transmit precoders for fixed \me{\mvec{w}{l,k,n}} is given by
\begin{IEEEeqnarray}{CCl}\label{eqn-mse-2} \neqsub
\underset{\substack{t_{l,k,n},\mvec{m}{l,k,n},\epsilon_{l,k,n}}}{\text{minimize}} &\quad& \|  \tilde{\mbf{v}}^{\prime}  \|_q \IEEEyessubnumber \label{eqn-mse-2.1} \\
\text{subject to} & \quad & \eqref{eqn-mse-1.3},\eqref{eqn-mse-1.4},\,\text{and} \:\eqref{mse-lin}. \IEEEyessubnumber \label{eqn-mse-2.2}
\end{IEEEeqnarray}
For fixed receivers, transmit precoders are obtained by solving \eqref{eqn-mse-2} iteratively by updating \me{\tilde{\epsilon}_{l,k,n}} with \me{{\epsilon}_{l,k,n}} found in previous iteration until termination as discussed in Section \ref{sec-3.2.1}.

In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step. Note that the feasible set of problems \eqref{eqn-3} and \eqref{eqn-mse-1} are bounded. However, the feasible set of \eqref{eqn-6} need not be bounded due to the introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Therefore, by restricting \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}}, the feasible set can be bounded without altering the solution space of other variables. However, as a consequence of considering the regularized objective in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}. With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}

%In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}. The quadratic term in the objective ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step. Even though the feasible set of \eqref{eqn-3} and \eqref{eqn-mse-2} are bounded, the feasible set of \eqref{eqn-6} need not be bounded due to the newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}. Since, \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. However, it can be avoided by bounding \eqn{\beta_{l,k,n}}'s with a maximum interference value depending on \eqn{P_{\max}}. By doing so, the domain of other variables are not affected by restricting \eqn{\beta_{l,k,n}}. Alternatively, if \eqref{mod_obj} is used instead of \eqref{eqn-6.1}, then the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}. With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}

%In all our simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. \reviewF{However, for a formal convergence analysis, we consider a regularized objective in \eqref{mod_obj} for \eqref{eqn-6.1} and \eqref{eqn-mse-1.1}. The proximal term in \eqref{mod_obj} ensures strong convexity, thereby enforcing the uniqueness of minimizer in each step. Even though the feasible set of \eqref{eqn-3} and the relaxed problem in \eqref{eqn-mse-1} are bounded, the feasible set of \eqref{eqn-6} need not be bounded due to the newly introduced variables in \eqref{eqn-6.2} and \eqref{eqn-6.3} to relax \eqref{eq:SINR}. Since, \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating any other constraints in \eqref{eqn-6} when \eqn{\gamma_{l,k,n} = 0}. Note that it can be avoided by bounding \eqn{\beta_{l,k,n}}'s with a maximum interference constraint depending on \eqn{P_{\max}} without altering the solution space of other variables. However, as a consequence of considering a regularized objective as in \eqref{mod_obj}, the additional constraint is not required, since \eqn{\beta_{l,k,n}} is bounded due to the proximal term in \eqref{mod_obj}. With the above assumptions, convergence proof is presented in Appendix \ref{sec-3.5}.}

%In all simulations, objective sequence generated by Algorithm \ref{algo-1} converges. \reviewF{However, for formal convergence analysis, following alterations are assumed. (i) Instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}, we consider a regularized objective as in \eqref{mod_obj} to ensure uniqueness of the minimizer in each step. (ii) Even though the feasible set of \eqref{eqn-3} is compact, it is due to the newly introduced variables in \eqref{eqn-6}, the feasible set in \eqref{eqn-9} and \eqref{eqn-9--1} can become unbounded. Since when \eqn{\gamma_{l,k,n} = 0}, \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating other constraints. Therefore, to bound \eqn{\beta_{l,k,n}}, we introduce an additional constraint to limit \eqn{\beta_{l,k,n}} for some large \eqn{B_{\max} \gg P_{\max}} as \eqn{\beta_{l,k,n} \leq B_{\max}} without altering the problem. Now, with these assumptions, convergence proof is dealt in Appendix \ref{sec-3.5}.}

%Note that due to the newly introduced variables in \eqref{eqn-6}, the feasible set of \eqref{eqn-9} and \eqref{eqn-9--1} can become unbounded even if the feasible set of \eqref{eqn-3} is bounded. It happens only when \eqn{\gamma_{l,k,n} = 0}, since \eqn{\beta_{l,k,n}} can assume any value satisfying \eqref{eqn-6.3} without violating other constraints in \eqref{eqn-6}. However, as a result of using \eqref{mod_obj}, the feasible set of \eqref{eqn-9} and \eqref{eqn-9--1} are always bounded. Now, by using the modified objective in \eqref{mod_obj}, convergence of Algorithm \ref{algo-1} is dealt in Appendix \ref{sec-3.5}.}

%In all our numerical simulations, the objective sequence generated by the Algorithm \ref{algo-1} converges. However, for a theoretical convergence analysis, we consider a regularized objective function as in \eqref{mod_obj} instead of \eqref{eqn-6.1} and \eqref{eqn-mse-2.1}. The proximal term in \eqref{mod_obj} is introduced to guarantee strict monotonicity of the objective function, thereby ensuring unique minimizer in every \ac{SCA} and \ac{AO} step. By using the modified objective function in \eqref{mod_obj}, the convergence analysis of the proposed iterative algorithms is discussed in Appendix \ref{sec-3.5}.

### 2015-11-13 Report/sub_channel_wsrm.tex
updated response document and manuscript

The complexity of the \ac{JSFRA} algorithm scales quickly with the number of sub-channels, since the complexity of an interior point method, which is used to solve the problem, increases with the problem size. Thus, we can use the decomposition methods presented in \cite{palomar2006tutorial,boyd2011distributed} to overcome this complexity by designing precoders for each sub-channels independently with minimal information exchange.

>>>>

The \ac{JSFRA} algorithm complexity scales with the number of sub-channels, since the complexity of interior point method, used to solve the problem, increases with the problem size. Thus, we can use the decomposition methods in \cite{palomar2006tutorial,boyd2011distributed} for designing precoders of each sub-channel with less complexity by using additional coupling variables among the subproblems.

### 2015-11-13 Report/wsrm_formulation.tex
updated response document and manuscript

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find transmit precoders by solving \eqref{eqn-9}. For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}. Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be the solution of \eqref{eqn-9} in the \eqn{\ith{(j-1)}} \ac{SCA} step. Since \ac{SCA} is an iterative procedure, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is updated as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}. Note that \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is obtained by solving either \eqref{opt-rx} or by using \eqref{eqn-10} from the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

Upon convergence of objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from previous \ac{SCA} step. Once the receivers are updated, transmit precoders are again evaluated with the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}. The above procedure is repeated until \eqn{i \to \infty} or for some fixed \eqn{I_{\max}} as outlined in Algorithm \ref{algo-1}.

The initial feasible point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user beamformers satisfying the total power constraint \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are obtained using \ac{MMSE} receivers in \eqref{eqn-10}. Now, by using fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c} for all users.

>>>>

Let us consider the \eqn{\ith{j}} \ac{SCA} iteration in the \eqn{\ith{i}} \ac{AO} step to find transmit precoders by solving \eqref{eqn-9}. For brevity, let us consider \eqn{\mbf{m}} as the collection of all transmit precoders as \eqn{\mbf{m} = \{\mvec{m}{l,k,n}\}_{\forall l,\forall k, \forall n}}. Similarly, we denote \eqn{\mbf{w}} and \eqn{\mbfa{\beta}} as \eqn{\{\mvec{w}{l,k,n}\}_{\forall l,\forall k, \forall n}} and \eqn{\{\mvec{\beta}{l,k,n}\}_{\forall l,\forall k, \forall n}} respectively. Let \eqn{\{\mbf{m}^{(i)}_{j}, \mbfa{\beta}^{(i)}_{j}\}} be a minimizer obtained in the \eqn{\ith{(j-1)}} \ac{SCA} step. Since \ac{SCA} is an iterative scheme, the next operating point \eqn{\tilde{\mbf{u}}_{l,k,n}} for the \eqn{\ith{(j+1)}} step is given as \eqn{\mbf{z}^{(i)}_{j} \triangleq \{\mbf{m}^{(i)}_{j}, \mbf{w}^{(i-1)}_{\lpointx}, \mbfa{\beta}^{(i)}_{j} \}}. Note that  \eqn{\mbf{w}^{(i-1)}_{\lpointx}} is obtained by solving either \eqref{opt-rx} or by using \eqref{eqn-10} in the \eqn{\ith{(i-1)}} \ac{AO} step.
\begin{algorithm}
	\SetAlgoLined
	\DontPrintSemicolon
	\BlankLine
	\SetKwInput{KwInit}{Initialize}
	\KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{N}}}
	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
	\KwInit{\me{i=0,j=0} and \me{\tilde{\mbf{m}}_{l,k,n}} using single user beamformer satisfying power constraint \eqref{eqn-9.1d}}
	update \me{\tilde{\mbf{w}}_{l,k,n}, \tilde{\mbf{\beta}}_{l,k,n}} using \eqref{eqn-10} and \eqref{eqn-9.1c} with \me{\tilde{\mbf{m}}_{l,k,n}} \;
	\Repeat{Queue convergence or \me{i \geq I_{\max}}}{
		\Repeat{\ac{SCA} convergence or \me{j \geq K_{\max}}}{
			solve for the transmit precoders \me{\mvec{m}{l,k,n}} using \eqref{eqn-9}\;
			update the constraint set \eqref{eqn-8} with \me{{\mbf{u}}_{l,k,n}} and \me{\mvec{m}{l,k,n}} using \eqref{eqn-wsrm-expr} and increment $j = j + 1$\;
		}
		update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-9--1} or \eqref{eqn-10} with the updated precoders \me{\mvec{m}{l,k,n}}\;
		$i = i + 1$, \me{j = 0}\;
	}
	\caption{Algorithm of \acs{JSFRA} scheme}
	\label{algo-1} 
\end{algorithm}

Upon convergence of the objective sequence, receivers are updated using fixed transmit precoders \eqn{\mbf{m}^{(i)}_{\lpointx}} obtained from the previous \ac{SCA} step. Once the receivers are updated, transmit precoders are again evaluated using the newly found receivers by solving \eqref{eqn-9} or \eqref{eqn-10}. The above procedure is repeated until \eqn{i \to \infty} or for some fixed \eqn{I_{\max}} as outlined in Algorithm \ref{algo-1}.

A feasible initial point \me{\tilde{\mbf{u}}_{l,k,n}} is obtained by fixing \me{\tilde{\mbf{m}}_{l,k,n}} with the respective single-user precoders satisfying total power constraint in \eqref{eqn-9.1d} and \me{\tilde{\mbf{w}}_{l,k,n}}'s are updated by using the \ac{MMSE} receiver in \eqref{eqn-10}. Now, for fixed transmit and receive beamformers, \me{\tilde{\mbf{\beta}}_{l,k,n}}'s are evaluated using \eqref{eqn-9.1c}.

### 2015-11-13 Response/Response 3/additions.tex
updated response document and manuscript

\begin{enumerate}
	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the proposed algorithm.
	\item We have updated the convergence of distributed algorithm to reflect the same.
	\item We included additional constraints on optimization variables to ensure compactness of feasible set in each subproblem
\end{enumerate}

@@

>>>>

\begin{enumerate}
	\item We have rewritten Appendix A-D to discuss the stationarity of limit points of the sequence of beamformer iterates generated by the centralized algorithms.
	\item We have updated the convergence of distributed algorithm to reflect the same.
\end{enumerate}

@@

\subsection*{List of Changes:}
\vspace*{1eM}
\begin{itemize}
	\item Page 6, paragraph after (28)
	\item Page 8, \eqn{\ith{13}} line on last paragraph in Section IV-B
	\item Page 12, paragraph following itemized requirements in Appendix A
	\item Last sentence after (51) on page 14
	\item Last paragraph in Appendix A-C
	\item Appendix A-D is rewritten using subsequence convergence
	\item Last sentence after (60) on page 15
\end{itemize}
